Graph Testing

### 2020-02-24 notes/graph_testing.tex
updated main notes

We want to apply Lemma~\ref{lem:fixed_graph_testing} to the case where $G = G_{n,r}$. In order to do this, we will need to show that when $r$ and $\kappa$ are appropriately tuned and $\norm{f}_{\Leb^2(\mathcal{X})}$ is sufficiently large, the inequality~\eqref{eqn:fixed_graph_testing_critical_radius} holds with respect to $G = G_{n,r}$ and $\beta = (f(x_1),\ldots,f(x_n))$. In particular, we will show that the following statements each hold with probability at least $1 - c/b$ for sufficiently large $n$ (Here and in what follows, $c$ denotes a constant which is fixed in $n$ and $f$ and does not depend on $b$, but may depend on other fixed quantities such as $d$, $s$, etc.): 
\begin{enumerate}[label=(E\arabic*)]
	\item 
	\label{event:discrete_sobolev_norm}
	\textbf{Graph Sobolev norm:} For any $n^{-1/(2(s - 1) + d)}\leq r$ such that $r \to 0$ as $n \to \infty$,
	\begin{equation}
	\label{eqn:continuous_to_discrete_sobolev_norm}
	f^T L^s f \leq c \cdot b \cdot \norm{f}_{H^s(\Xset)}^2 \cdot n^{s + 1} r^{s(d + 2)}.
	\end{equation}
	for all $n$ sufficiently large.
	\item 
	\label{event:eigenvalue_tail_decay_2}
	\textbf{Eigenvalue tail bound:} There exists a constant $c$ such that for any $\kappa = 1,\ldots,n$, if $\max\{ 3 d_{\infty}(X,\ol{X}),n^{-1/d}\} \leq r \leq \kappa^{-2/(d(2 +d))}$ then,
	\begin{equation}
	\label{eqn:eigenvalue_tail_bound_2}
	\lambda_{\kappa} \geq c \cdot n r^{d + 2} \kappa^{2/d}
	\end{equation}
	In particular, the inequality~\eqref{eqn:eigenvalue_tail_bound_2} is satisfied for sufficiently large $n$ when $\kappa = n^{2d/(4s + d)}$ and $c(\log n/n)^{1/d} \leq r \leq n^{-4/((2+d)(4s + d))}$. 
	\item 
	\label{event:l2_norm_order1}
	\textbf{Empirical norm of $f$:} There exists a constant $c_1$ such that if $\norm{f}_{\Leb^2(\Xset)} \geq c_1 \cdot b \cdot n^{-2s/(4s + d)}$ and $4s > d$, then
	\begin{equation}
	\label{eqn:l2_to_empirical_norm_order1}
	\norm{f}_n^2 \geq \frac{1}{b} \cdot \norm{f}_{\Leb^2}^2
	\end{equation}
\end{enumerate}

@@

The following Lemma helps us deal with remainder terms in the Sobolev case.
\begin{lemma}
	\label{lem:remainder_term_sobolev}
	Suppose $f \in \Leb^2(U_r)$ and $k \in (n)$. Then,
	\begin{equation*}
	\norm{\Ebb\bigl[D_kf\bigr]}_{\Leb^2(U)}, \norm{\Ebb\bigl[fK_r(x_k,\cdot)\bigr]}_{\Leb^2(U)} \leq c \norm{f}_{\Leb^2(U_r)}
	\end{equation*}
\end{lemma}

>>>>

We want to apply Lemma~\ref{lem:fixed_graph_testing} to the case where $G = G_{n,r}$. In order to do this, we will need to show that when $r$ and $\kappa$ are appropriately tuned and $\norm{f}_{\Leb^2(\mathcal{X})}$ is sufficiently large, the inequality~\eqref{eqn:fixed_graph_testing_critical_radius} holds with respect to $G = G_{n,r}$ and $\beta = (f(x_1),\ldots,f(x_n))$. In particular, we will show that the following statements each hold with probability at least $1 - c/b$ for sufficiently large $n$ (Here and in what follows, $c$ denotes a constant which is fixed in $n$ and $f$ and does not depend on $b$, but may depend on other fixed quantities such as $d$, $s$, etc.): 
\begin{enumerate}[label=(E\arabic*)]
	\item 
	\label{event:discrete_sobolev_norm}
	\textbf{Graph Sobolev norm:} There exists an $r^{\star}$ (which does not depend on $f$) such that for any $n^{-1/(2(s - 1) + d)}\leq r \leq r^{\star}$,
	\begin{equation}
	\label{eqn:continuous_to_discrete_sobolev_norm}
	f^T L^s f \leq c \cdot b \cdot \norm{f}_{H^s(\Xset)}^2 \cdot n^{s + 1} r^{s(d + 2)}.
	\end{equation}
	\item 
	\label{event:eigenvalue_tail_decay_2}
	\textbf{Eigenvalue tail bound:} There exists a constant $c$ such that for any $\kappa = 1,\ldots,n$, if $\max\{ 3 d_{\infty}(X,\ol{X}),n^{-1/d}\} \leq r \leq \kappa^{-2/(d(2 +d))}$ then,
	\begin{equation}
	\label{eqn:eigenvalue_tail_bound_2}
	\lambda_{\kappa} \geq c \cdot n r^{d + 2} \kappa^{2/d}
	\end{equation}
	In particular, the inequality~\eqref{eqn:eigenvalue_tail_bound_2} is satisfied for sufficiently large $n$ when $\kappa = n^{2d/(4s + d)}$ and $c(\log n/n)^{1/d} \leq r \leq n^{-4/((2+d)(4s + d))}$. 
	\item 
	\label{event:l2_norm_order1}
	\textbf{Empirical norm of $f$:} There exists a constant $c_1$ such that if $\norm{f}_{\Leb^2(\Xset)} \geq c_1 \cdot b \cdot n^{-2s/(4s + d)}$ and $4s > d$, then
	\begin{equation}
	\label{eqn:l2_to_empirical_norm_order1}
	\norm{f}_n^2 \geq \frac{1}{b} \cdot \norm{f}_{\Leb^2}^2
	\end{equation}
\end{enumerate}

@@

The following Lemma helps us deal with remainder terms in the Sobolev case.
\begin{lemma}
	\label{lem:remainder_term_sobolev}
	Let $U \subset \Rd$ be an open set, and $U_r = \set{x \in \Rd: \mathrm{dist}(x,U) < x}$. Suppose $f \in \Leb^2(U_r)$ and $k \in (n)$. Then,
	\begin{equation*}
	\norm{\Ebb\bigl[D_kf\bigr]}_{\Leb^2(U)}, \norm{\Ebb\bigl[fK_r(x_k,\cdot)\bigr]}_{\Leb^2(U)} \leq c \norm{f}_{\Leb^2(U_r)}
	\end{equation*}
\end{lemma}
